---
title: "Hollywood_Highest_Gross_Movies"
author: "Skillarchie Davis"
date: '2022-05-02'
output:
  html_document:
    df_print: paged
  pdf_document: default
---


## The libraries necessary for data cleaning
```{r}
# text mining library
library(tidyverse)
library(lubridate)
library('pracma')
library(tm)
library(corrplot)
library(reshape2)
library("tm")
library(syuzhet)
library(plotly)
```

## Data Preprocessing

### Loading in the dataset
```{r}
Movies <- read_csv("C:/Users/skill/Desktop/Highest Holywood Grossing Movies.csv")
```

### Step 1: Initial Exploratory Analysis
```{r}
Movies_clean <- Movies
```

```{r}
dim(Movies_clean)
```


```{r}
head(Movies_clean)
```


```{r}
glimpse(Movies_clean)
```

### Delete Columns that won't help with analysis.
```{r}
Movies_clean$...1 <- Movies_clean$`Movie Info` <- Movies_clean$`Movie Runtime` <- NULL
```

```{r}
glimpse(Movies_clean)
```

```{r}
Movies_clean$Genre[1:5]
```


```{r}
# Rename columns Domestic.Sales..in...
Movies_clean <- rename(Movies_clean, c("Domestic_Sales" =`Domestic Sales (in $)`, "International_Sales" = `International Sales (in $)`, "World_Sales" = `World Sales (in $)`))
```

```{r}
colnames(Movies_clean[4:6]) 
```

```{r}
# Divide sale by 1 million for better readability
Movies_clean$Domestic_Sales <- ceil(Movies_clean$Domestic_Sales / 1000000)
Movies_clean$International_Sales <- ceil(Movies_clean$International_Sales / 1000000)
Movies_clean$World_Sales <- ceil(Movies_clean$World_Sales / 1000000)
```


```{r}
head(Movies_clean[4:6])
```


```{r}
# Checking for duplicate movie names
any(duplicated(Movies_clean$Title))
```


### Summary Statistics for all the columns of the data frame
```{r}
summary(Movies_clean[4:6])
```

### Step 2: Visual Exploratory Analysis
```{r}
hist(Movies_clean$Domestic_Sales)
hist(Movies_clean$International_Sales)
hist(Movies_clean$World_Sales)
```


```{r}
boxplot(Movies_clean$Domestic_Sales)
boxplot(Movies_clean$International_Sales)
boxplot(Movies_clean$World_Sales)
```

### Checking for NA's
```{r}
any(is.na(Movies_clean))
```

```{r}
apply(Movies_clean, 2,function(x) sum(is.na(x)))
```

```{r}
unique(Movies_clean$License)
```

### Step 3: Correcting the errors!
```{r}
Movies_clean <- Movies_clean %>% 
                mutate(License = replace_na(License, "Not Rated"))
```

### Working with strings
```{r}
# Trim columns with character datatype
Movies_clean$Title <- str_trim(Movies_clean$Title)
Movies_clean$Distributor <- str_trim(Movies_clean$Distributor)
Movies_clean$Genre <- str_trim(Movies_clean$Genre)
Movies_clean$License <- str_trim(Movies_clean$License)
```


```{r}
unique(Movies_clean$License)
```

## Data Transformation

### Working with dates
```{r}
# Getting the Year the movie was release from the title
Movies_clean$Years <- str_sub(Movies_clean$Title,start = -5, end = -2)
```

```{r}
any(is.na(Movies_clean$Years))
```


```{r}
head(Movies_clean$Years)
```

```{r}
Movies_clean$Date <- mdy(Movies_clean$`Release Date`)
```


```{r}
## First make up some mock data
my_data <- data.frame(date = seq(as.Date("2010-01-01"), as.Date("2015-12-31"), 
                                by = "1 month"), 
                     value = rnorm(72))

## Remove some observations so we have an incomplete data set
my_incomplete_data <- my_data[sort(sample(nrow(my_data), 60)), ]
```



```{r}
# Filling missing dates with the sample dates
Movies_clean$Date [is.na(Movies_clean$Date)] <- seq(min(my_incomplete_data$date), max(my_incomplete_data$date), 
                  by = "3 month")
```


```{r}
any(is.na(Movies_clean$Date))
```


```{r}
# Extracting months from dates
#Movies_clean$Months <-months(Movies_clean$Date, abbreviate = TRUE)
#https://epirhandbook.com/en/working-with-dates.html
#months(Movies_clean$Date, abbreviate = TRUE)
Movies_clean$Months <- format(Movies_clean$Date, format = "%b")
Movies_clean$Months <- factor(Movies_clean$Months, levels = month.abb)
```


```{r}
head(Movies_clean$Months)
```


```{r}
# Extracting days of the week from dates
Days <- c("Sunday", "Monday","Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
Movies_clean$Day_of_Week <- weekdays(Movies_clean$Date)
Movies_clean$Day_of_Week <- factor(Movies_clean$Day_of_Week, levels = Days)
```

```{r}
head(Movies_clean$Day_of_Week)
```


```{r}
# Drop the release date column 
Movies_clean$`Release Date` <- NULL
```

# Data Analysis

```{r}
Movies_Analysis <- Movies_clean
```

### The total movie sales by license type
```{r}
Movies_Analysis %>% group_by(License) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales))
```

### The median of movie sales by license type
```{r}
Movies_Analysis %>% group_by(License) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = median(Domestic_Sales),
                                                 International =median(International_Sales),
                                                 World = median(World_Sales))
```



### The total movie sales by Distributor
```{r}
df <- Movies_Analysis %>% group_by(Distributor) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales))
df[order(df$Movie_Amount, decreasing = TRUE),]
```

### The median of movie sales by Distributor
```{r}
df <- Movies_Analysis %>% group_by(Distributor) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = median(Domestic_Sales),
                                                 International =median(International_Sales),
                                                 World = median(World_Sales))
df[order(df$World, decreasing = TRUE),]
```


### Top ten film by world sales
```{r}
Movies_Analysis %>% group_by(Title) %>% summarise(Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) %>% top_n(10,World)
```

### The total movie sales by Years
```{r}
Movies_Analysis %>% group_by(Years) %>% summarise(  Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) %>% top_n(11,World)
```

### The total movie sales by Months
```{r}
Movies_Analysis %>% group_by(Months) %>% summarise( Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) 
```

### The total movie sales by Weekday
```{r}
Movies_Analysis %>% group_by(Day_of_Week) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) 
```

### Best selling movie
```{r}
Movies_Analysis %>% filter(Movies_Analysis$Domestic_Sales == max(Movies_Analysis$Domestic_Sales)) #%>% select(Title,Genre)
```

### Least selling movies
```{r}
Movies_Analysis %>% filter(Movies_Analysis$Domestic_Sales == min(Movies_Analysis$Domestic_Sales)) #%>% select(Title,Genre)
```


## Deep dive analysis
```{r}
analysis_dive <-Movies_Analysis %>% filter(Years %in% c(2017,2018,2019))
```


### The total movie sales by license type
```{r}
analysis_dive %>% group_by(License) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales))
```

### The total number of movies by license group by distributors
```{r}
analysis_dive %>% group_by(Distributor,License) %>% summarise(Movie_Amount = n_distinct(Title),
                                                              Domestic = sum(Domestic_Sales)
                                                              ,.groups = 'drop')
```

### The total movie sales by top ten Distributor
```{r}
df <- analysis_dive %>% group_by(Distributor) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) %>% top_n(10,World)
df[order(df$Movie_Amount,decreasing = TRUE),]
```


### Top ten films by world sales
```{r}
analysis_dive %>% group_by(Title) %>% summarise(Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) %>% top_n(10,World)
```

### The total movie sales by Years
```{r}
analysis_dive %>% group_by(Years) %>% summarise(  Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) %>% top_n(11,World)
```

### The total movie sales by Months
```{r}
analysis_dive %>% group_by(Months) %>% summarise( Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) 
```

### The total movie sales by Weekday
```{r}
analysis_dive %>% group_by(Day_of_Week) %>% summarise(Movie_Amount = n_distinct(Title),
                                                 Domestic = sum(Domestic_Sales),
                                                 International =sum(International_Sales),
                                                 World = sum(World_Sales)) 
```

### Best selling movie
```{r}
analysis_dive %>% filter(Domestic_Sales == max(Domestic_Sales)) #%>% select(Title,Genre)
```

### Least selling movies
```{r}
analysis_dive %>% filter(Domestic_Sales == min(Domestic_Sales)) #%>% select(Title,Genre)
```


## Data Visualization
```{r}
movie_viz <- Movies_Analysis %>% filter(Years %in% c(2014,2015,2017,2018,2019))
```


```{r}
movie_viz %>% group_by(License) %>% summarise(Domestic = sum(Domestic_Sales)) %>% 
  ggplot(aes(x =License, y = Domestic, fill = License)) +
  labs(title = "Total Domestic Sales by license in Millions", x = "License", y = "Sales")+geom_col(position = "dodge")
```
```{r}
movie_viz %>% group_by(Day_of_Week) %>% summarise(Domestic = sum(Domestic_Sales)) %>% 
  ggplot(aes(x =Day_of_Week, y = Domestic, fill = Day_of_Week)) +
  labs(title = "Total Domestic Sales by Weekday in Millions ", x = "Week Days", y = "Sales")+geom_col(position = "dodge", show.legend = FALSE)
```

```{r}
movie_viz %>% group_by(Months) %>% summarise(Domestic = sum(Domestic_Sales)) %>% 
  ggplot(aes(x =Months, y = Domestic, fill = Months)) +
  labs(title = "Total Domestic Sales by Months in Millions", x = "Months", y = "Sales")+geom_col(position = "dodge")
```



```{r}
movie_viz %>% group_by(Years) %>% summarise(Domestic = sum(Domestic_Sales)) %>%
plot(type="l",col="blue", xlab = 'Years', ylab = 'Sales', main = 'Total Domestic Sales by Years in Millions')
```




```{r}
movie_viz <-subset(movie_viz, Date > '2010-12-31')
```

```{r}
year <-format(movie_viz$Date, format = "%Y")
```

```{r}
fig <- plot_ly(data = movie_viz, x = ~Date, y = ~Domestic_Sales, color = year,
               type = 'scatter', mode = 'markers', size = ~Domestic_Sales,fill = ~'',
marker = list(sizemode = 'diameter')) 

fig %>% layout(title = 'Total Domestic Sales by Years and Months in Millions',
         showlegend = FALSE)
```


```{r}
i <- movie_viz %>% group_by(Distributor) %>% summarise(Domestic = sum(Domestic_Sales)) %>% top_n(10,Domestic)
ggplot(i,aes(x = Domestic, y = fct_rev(Distributor), fill = Distributor)) +  theme_minimal()+
labs(title = "Total Domestic Sales by Distributors in Millions ", x = "Distributors", y = "Sales")+geom_col(position = "dodge",show.legend = FALSE)
```







## Linear Regression Model

### Searching for distributors that has less than 3 movies ad remove them.
```{r}
Movie_LM <-subset(Movies_Analysis, Years > '1999')
modelrdy <- Movie_LM %>% group_by(Distributor) %>% summarise(Amount = n_distinct(Title)) 
modelrdy[order(modelrdy$Amount,decreasing = FALSE),]
```

```{r}
weird <- c("FilmDistrict",
"Focus Features",
"20th Century Studios",
"IFC Films",	
"Newmarket Films",
"Relativity Media",
"Roadside Attractions",
"Sony Pictures Classics",
"United Artists",
"United Artists Releasing",
"USA Films")
```



```{r}
`%!in%` <- Negate(`%in%`)
```

```{r}
Regression <- Movie_LM %>% filter(Distributor %!in% weird)
testing <- Regression %>% select(Distributor,International_Sales,World_Sales,Years,Domestic_Sales)
```


```{r}
set.seed(1)
train <- sample(1:nrow(testing),nrow(testing)*0.8)
train_data <- testing[train,]
test_data <- testing[-train,]

result <- lm(Domestic_Sales ~Distributor+International_Sales+World_Sales+Years, data=train_data)

test_data$PredictDomesticSales <- predict(result,test_data[,1:5])

```


```{r}
summary(result)
```


```{r}
summary(test_data)
```
```{r}
#create fitted value vs residual plot
plot(fitted(result), residuals(result))

#add horizontal line at 0
abline(h = 0, lty = 2)
```

```{r}
hist(residuals(result), col = "steelblue")
```


```{r}
test_data$PredictDomesticSales <- predict(result,test_data[,1:4])
```

```{r}
predict(result,newdata = test_data,interval = 'confidence')
```

### Checking for correlation.
```{r}
cor(test_data$Domestic_Sales,test_data$PredictDomesticSales)
```


```{r}
line = list(color = "blue")
plot_ly(test_data, x = ~Domestic_Sales, y = ~PredictDomesticSales) %>%
  add_markers(color = ~line) %>%
  layout(xaxis=list(title=""), showlegend=FALSE,
         title="Visualisation of the predicted Domestic Sales and Domestic Sales")
```





```{r}
#write.csv(Movies_Analysis, 'C:\\Users\\Skill\\Desktop\\viz.csv')
```
















